Multi-modality Imagery Database for Plant Phenotyping

### 2015-04-14 datapaper_intro.tex
xm  edits

Plant image analysis is a non-trivial computer vision task, due to diverse variations of leaf appearance, overlapping and dynamics.
In order to develop advanced algorithms, image databases that are well representative of this application domain is highly important.
In fact, computer vision research lives on and advances with databases, as evidenced by the successful databases in the field (e.g., FERET~\cite{Phillips2000}, LFW~\cite{LFW}, Caltech$101$~\cite{Fei-Fei2004}).
However, the publicly available database on plant imagery is very limited, with the only exception of~\cite{scharr2014annotated} and~\cite{haug2014crop}.
Both databases have the limitations in that they only capture RGB images, and are suitable for a small set of tasks.

@@

In summary, this paper and our database have made the following main contribution. 
\begin{itemize}
\item MSU-PID is the first {\it multi-modality} plant image database. 
This allows researchers to study the strength and weakness of individual modality, as well as their fusion in plant image analysis.
\item Our imaging setup and the variety of manu labele make MSU-PID a candidate dataset for a diverse set of plant image analysis tasks, including leaf segementation, leaf counting, leaf alignment, leaf tracking, leaf growth prediction, etc.
\end{itemize}

>>>>

Plant image analysis is a non-trivial computer vision task, due to diverse variations of leaf appearance, overlapping and dynamics.
In order to develop advanced algorithms, image databases that are well representative of this application domain is highly important.
In fact, computer vision research lives on and advances with databases, as evidenced by the successful databases in the field (e.g., FERET~\cite{Phillips2000}, LFW~\cite{LFW}, Caltech$101$~\cite{Fei-Fei2004}).
However, the publicly available database for plant phenotyping is very limited, with the only exception of LSC database~\cite{scharr2014annotated}.
The LSC database has the limitations in that it only captures RGB images, and are suitable for a small set of applications.

@@

In summary, this paper and our database have made the following main contribution. 
\begin{itemize}
\item MSU-PID is the first {\it multi-modality} plant image database. 
This allows researchers to study the strength and weakness of individual modality, as well as their fusion in plant image analysis.
\item Our imaging setup and the variety of manu labele make MSU-PID an ideal candidate for evaluating a diverse set of plant image analysis tasks, including leaf segementation, leaf counting, leaf alignment, leaf tracking, leaf growth prediction, etc.
\end{itemize}
